Advances in Artificial Intelligence for Data Visualization: Developing Computer Vision Models to Automate Reading of Data Plots, with Application to Predictive Model Diagnostics

### 2024-07-01 Thesis/02-chap2.qmd
update thesis folder

```{=html}
<table style="margin-left: auto; margin-right: auto;">
<thead>
<tr>
<th style="border-bottom:hidden;padding-bottom:0; padding-left:3px;padding-right:3px;text-align: center; " colspan="2"><div style="border-bottom: 1px solid #ddd; padding-bottom: 5px; ">Non-linearity</div></th>
<th style="border-bottom:hidden;padding-bottom:0; padding-left:3px;padding-right:3px;text-align: center; " colspan="2"><div style="border-bottom: 1px solid #ddd; padding-bottom: 5px; ">Heteroskedasticity</div></th>
<th style="border-bottom:hidden;padding-bottom:0; padding-left:3px;padding-right:3px;text-align: center; " colspan="2"><div style="border-bottom: 1px solid #ddd; padding-bottom: 5px; ">Common</div></th>
</tr>
<tr>
<th style="border-bottom:hidden;padding-bottom:0; padding-left:3px;padding-right:3px;text-align: center; " colspan="1"><div style="border-bottom: 1px solid #ddd; padding-bottom: 5px; ">Poly Order (j)</div></th>
<th style="border-bottom:hidden;padding-bottom:0; padding-left:3px;padding-right:3px;text-align: center; " colspan="1"><div style="border-bottom: 1px solid #ddd; padding-bottom: 5px; ">SD (σ)</div></th>
<th style="border-bottom:hidden;padding-bottom:0; padding-left:3px;padding-right:3px;text-align: center; " colspan="1"><div style="border-bottom: 1px solid #ddd; padding-bottom: 5px; ">Shape (a)</div></th>
<th style="border-bottom:hidden;padding-bottom:0; padding-left:3px;padding-right:3px;text-align: center; " colspan="1"><div style="border-bottom: 1px solid #ddd; padding-bottom: 5px; ">Ratio (b)</div></th>
<th style="border-bottom:hidden;padding-bottom:0; padding-left:3px;padding-right:3px;text-align: center; " colspan="1"><div style="border-bottom: 1px solid #ddd; padding-bottom: 5px; ">Size (n)</div></th>
<th style="border-bottom:hidden;padding-bottom:0; padding-left:3px;padding-right:3px;text-align: center; " colspan="1"><div style="border-bottom: 1px solid #ddd; padding-bottom: 5px; ">Distribution of the fitted values</div></th>
</tr>
</thead>
<tbody>
  <tr>
   <td style="text-align:right;"> 2 </td>
   <td style="text-align:right;"> 0.25 </td>
   <td style="text-align:right;"> -1 </td>
   <td style="text-align:right;"> 0.25 </td>
   <td style="text-align:right;"> 50 </td>
   <td style="text-align:center;"> Uniform </td>
  </tr>
  <tr>
   <td style="text-align:right;"> 3 </td>
   <td style="text-align:right;"> 1.00 </td>
   <td style="text-align:right;"> 0 </td>
   <td style="text-align:right;"> 1.00 </td>
   <td style="text-align:right;"> 100 </td>
   <td style="text-align:center;"> Normal </td>
  </tr>
  <tr>
   <td style="text-align:right;"> 6 </td>
   <td style="text-align:right;"> 2.00 </td>
   <td style="text-align:right;"> 1 </td>
   <td style="text-align:right;"> 4.00 </td>
   <td style="text-align:right;"> 300 </td>
   <td style="text-align:center;"> Skewed </td>
  </tr>
  <tr>
   <td style="text-align:right;"> 18 </td>
   <td style="text-align:right;"> 4.00 </td>
   <td style="text-align:right;">  </td>
   <td style="text-align:right;"> 16.00 </td>
   <td style="text-align:right;">  </td>
   <td style="text-align:center;"> Discrete </td>
  </tr>
  <tr>
   <td style="text-align:right;">  </td>
   <td style="text-align:right;">  </td>
   <td style="text-align:right;">  </td>
   <td style="text-align:right;"> 64.00 </td>
   <td style="text-align:right;">  </td>
   <td style="text-align:center;">  </td>
  </tr>
</tbody>
</table>
```

>>>>

```{=html}
<table style="margin-left: auto; margin-right: auto;">
<thead>
<tr>
<th style="border-bottom:hidden;padding-bottom:0; padding-left:3px;padding-right:3px;text-align: center; " colspan="2"><div style="border-bottom: 1px solid #ddd; padding-bottom: 5px; ">Non-linearity</div></th>
<th style="border-bottom:hidden;padding-bottom:0; padding-left:3px;padding-right:3px;text-align: center; " colspan="2"><div style="border-bottom: 1px solid #ddd; padding-bottom: 5px; ">Heteroskedasticity</div></th>
<th style="border-bottom:hidden;padding-bottom:0; padding-left:3px;padding-right:3px;text-align: center; " colspan="2"><div style="border-bottom: 1px solid #ddd; padding-bottom: 5px; ">Common</div></th>
</tr>
<tr>
<th style="border-bottom:hidden;padding-bottom:0; padding-left:3px;padding-right:3px;text-align: center; " colspan="1"><div style="border-bottom: 1px solid #ddd; padding-bottom: 5px; " data-qmd="Poly Order ($j$)"></div></th>
<th style="border-bottom:hidden;padding-bottom:0; padding-left:3px;padding-right:3px;text-align: center; " colspan="1"><div style="border-bottom: 1px solid #ddd; padding-bottom: 5px; " data-qmd="SD ($\sigma$)"></div></th>
<th style="border-bottom:hidden;padding-bottom:0; padding-left:3px;padding-right:3px;text-align: center; " colspan="1"><div style="border-bottom: 1px solid #ddd; padding-bottom: 5px; " data-qmd="Shape ($a$)"></div></th>
<th style="border-bottom:hidden;padding-bottom:0; padding-left:3px;padding-right:3px;text-align: center; " colspan="1"><div style="border-bottom: 1px solid #ddd; padding-bottom: 5px; " data-qmd="Ratio ($b$)"></div></th>
<th style="border-bottom:hidden;padding-bottom:0; padding-left:3px;padding-right:3px;text-align: center; " colspan="1"><div style="border-bottom: 1px solid #ddd; padding-bottom: 5px; " data-qmd="Size ($n$)"></div></th>
<th style="border-bottom:hidden;padding-bottom:0; padding-left:3px;padding-right:3px;text-align: center; " colspan="1"><div style="border-bottom: 1px solid #ddd; padding-bottom: 5px; " data-qmd="Distribution of the fitted values"></div></th>
</tr>
</thead>
<tbody>
  <tr>
   <td style="text-align:right;"> 2 </td>
   <td style="text-align:right;"> 0.25 </td>
   <td style="text-align:right;"> -1 </td>
   <td style="text-align:right;"> 0.25 </td>
   <td style="text-align:right;"> 50 </td>
   <td style="text-align:center;"> Uniform </td>
  </tr>
  <tr>
   <td style="text-align:right;"> 3 </td>
   <td style="text-align:right;"> 1.00 </td>
   <td style="text-align:right;"> 0 </td>
   <td style="text-align:right;"> 1.00 </td>
   <td style="text-align:right;"> 100 </td>
   <td style="text-align:center;"> Normal </td>
  </tr>
  <tr>
   <td style="text-align:right;"> 6 </td>
   <td style="text-align:right;"> 2.00 </td>
   <td style="text-align:right;"> 1 </td>
   <td style="text-align:right;"> 4.00 </td>
   <td style="text-align:right;"> 300 </td>
   <td style="text-align:center;"> Skewed </td>
  </tr>
  <tr>
   <td style="text-align:right;"> 18 </td>
   <td style="text-align:right;"> 4.00 </td>
   <td style="text-align:right;">  </td>
   <td style="text-align:right;"> 16.00 </td>
   <td style="text-align:right;">  </td>
   <td style="text-align:center;"> Discrete </td>
  </tr>
  <tr>
   <td style="text-align:right;">  </td>
   <td style="text-align:right;">  </td>
   <td style="text-align:right;">  </td>
   <td style="text-align:right;"> 64.00 </td>
   <td style="text-align:right;">  </td>
   <td style="text-align:center;">  </td>
  </tr>
</tbody>
</table>
```
